Viability of FTIR on fossil pollen

### 2020-10-07 manuscript.Rmd
wrote on introduction

# Introduction
Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age

# Methods and Materials
## Labwork Report

@@

@@

>>>>

Research Questions:
1. chemical variation between taxa in the same cores.
2. chemical variation between taxa between cores 
3. chemical variation of pollen with depths/age

## Labwork Report

@@

# TODO

- extract fresh Pinus from images
- measure samples from 2 more cores (9 each)
- mark Alnus and BetCor on images
- extract Alnus BetCor from Dal samples
- extract fresh Alnus BetCor

@@

Main Goal: Explore the chemical differences between fresh and untreated fossil pollen.

The study of plant remains is an integral part of Palaeoecology and Palaeobotany.
Spores and pollengrains, besides macrofossils, are utilized to study past environmental and climatic change, migration of plant communities as well as the development and evolution of plants. 
EXAMPLES

Pollen has shown to be resistant to diagenetic processes and found in most palaeoecological records.

FTIR used on fossil papers in the past use acetolysed pollen or other chemically extracted pollen. 
There has not been a comparison between fresh and untreated fossil pollen.
In order to compare which compounds are missing and still present in fossil pollen.

RQs
i. Difference between fresh and fossil grains.
ii. effect of orientation and depth/age on chemistry
iii. difference to other species
    -> needs extracting of spectra from files (marking of grains on images)
    -> add another core
